### 2020-03-11 document/manuscript-out.tex
Travis build: 128
Travis build: 129

\textbf{Placeholder Text for the Background}

@@

\section*{DataMining Section}\label{datamining-section}
\addcontentsline{toc}{section}{DataMining Section}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The publishing trend of Kenyan researchers. The trend indicates that
  open access publishing is popular. The popular journals where Kenyan
  researcher publish are open access.
\item
  Pre-prints. \textbf{\emph{more work needed here to find out whether
  they have embraced preprints and if so, who is driving the adoption?}}
\item
  Open data and Code.
  \textbf{\emph{\href{https://github.com/BioinfoNet/Data-mining/issues/11}{This
  is yet to be completed}. We need to find out whether Kenyan authors
  are making the data and code available and accessible, and whether
  they are adhering to the FAIR principles}}
\item
  Collaboration trends. Are Kenyan authors collaborating from within or
  without? This milestone is still pending. 5 What else?
\end{enumerate}

@@

To address this problem, we created a resource that can guide ECR and
students on where they publish open access, and at low cost. We also
provide information on how they can still be open when they publsih in
paywalled journals, eg via the green route.

@@

What is the take-home message from this article? What are the
recommendations? - The need for a framework to guide the adoption of
open science practices. Take note of the bariers and provide
recommendations. - The need for low-cost publishing - The need for
policies on open science that can be implemented by various
insituitions. For example, we can provide a template that can be adopted
by most instituitions

@@

We acknowledge the support from \ldots{} and the contribution from
Mozilla Science Lab and KENET.

>>>>

\textbf{Placeholder Text for the Background} WILL UPDATE TO INTRODUCTION

@@

\section*{Data Mining Section}\label{data-mining-section}
\addcontentsline{toc}{section}{Data Mining Section}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The publishing trend of Kenyan researchers. The trend indicates that
  open access publishing is popular. The popular journals where Kenyan
  researcher publish are open access.
\item
  Pre-prints. Pre-prints are yet to be widely adopted by Kenyan
  scientists and foreign collaborators drive the adoption of pre-prints
  among Kenyan authors
\item
  Open data and Code.
  \textbf{\emph{\href{https://github.com/BioinfoNet/Data-mining/issues/11}{This
  is yet to be completed}. We need to find out whether Kenyan authors
  are making the data and code available and accessible, and whether
  they are adhering to the FAIR principles}}
\item
  Collaboration trends. Are Kenyan authors collaborating from within or
  without? (based on pre-prints from bioRXiv, we see that Kenyan authors
  are mostly collaborating internationally. Is this the case from the
  rest of literature obtained during data mining?) 5 What else?
\end{enumerate}

@@

To address this problem, we created a resource that can guide ECR and
students on where they publish open access, and at low cost. We also
provide information on how they can still be open when they publish in
paywalled journals, eg via the green route.

@@

What is the take-home message from this article? What are the
recommendations? - The need for a framework to guide the adoption of
open science practices. Take note of the barriers and provide
recommendations. - The need for low-cost publishing - The need for
policies on open science that can be implemented by various
institutions. For example, we can provide a template that can be adopted
by most institutions

@@

We acknowledge the support from \ldots{} and the contribution from
Mozilla Science Lab and KENET, and ICIPE.
